\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time Projection Chamber for CLAS at JLab}

### 2016-09-16 eg6-letters/NIM/EG6_RTPC_NIM.tex
clean the NIM paper directory and writing

\documentclass[reprint, amsmath,amssymb, aps]{revtex4}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage{array}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{float}
\usepackage{wrapfig}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

@@

\preprint{APS/123-QED}

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time Projection Chamber for CLAS at JLab}}
\author{
\Large{R. Dupr\'e$^{1,2}$, N. Baltzell$^{1,3}$, K. Hafidi$^{1}$, M.  
Hattawy$^{1,2}$, S. Stepanyan$^{3}$} \\
\vspace{+5mm}
\normalsize $^{1}$ Argonne National Laboratory, Argonne IL 60439, USA \\
\normalsize $^{2}$ Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and 
Universit$\acute{e}$ Paris Sud, Orsay, France \\
\normalsize $^{3}$ Jefferson Laboratory, Newport News, VA 230606, USA.
}

\collaboration{CLAS Collaboration}

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\vspace{+25mm}
\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
processes, $^4$He remains intact and recoils as a whole in the final state. 
This experiment has been carried out using CEBAF Large Acceptance Spectrometer 
(CLAS) at JLab. The CLAS spectrometer has been used for similar studies on 
proton targets, however it cannot track recoils with momenta less than 250 
MeV/c.  We developed for an experiment in 2009 a Radial Time Projection Chamber 
(RTPC) based on Gas Electron Multipliers (GEMs).  The detector was positioned 
directly around the gaseous target of the experiment, allowing a detection 
threshold of $~$???  MeV/c for $^4$He. We describe in this article the design 
of the RTPC, the methods we developed to calibrate it and finally its 
performances.
\end{abstract}

@@

This paper is organized in this way: section $\RNum{2}$ details the design and the internal structure of the RTPC, while section $\RNum{3}$ points the properties of the readout system. The calibration strategies for such detectors will be discussed in section $\RNum{4}$. Finally, performances are discussed in section $\RNum{5}$.

\section{Design}

@@

\section{Readout System}
The RTPC electron collecting system has 3200 readout pads. These collection elements are located at the end of the amplification region, 69 mm from the central axis.
\begin{figure}[tb]
\centering
%\hspace{-1 cm}
\includegraphics[scale=0.55]{fig/PADs.png}
\caption[]{\small\sf A schematic representation of a part of the readout system. The shaded sixteen pads are a group of pads that are connected to the same pre-amplifier.} 
\label{fig:PADs}
\end{figure}
Figure \ref{fig:PADs} shows a schematic drawing of the size and the alignment configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in width the shift between the rows allows to reduce aliasing. Each half of the RTPC has 40 rows and 40 columns of pads. The shaded region in the figure~\ref{fig:PADs} shows how pads are grouped to the 16 channels pre-amplifiers. The Time to Digital Converter (TDC) units are 114~ns and indicates the time taken by the electron to drift from the ionization point to the readout board. On the the other side, the charge information is measured in Analog-to-Digital-Converter (ADC) units without specific normalization.

@@

\section{Calibration}
Two quantities are recorded for each detected electron at the readout board, time (TDCs) and signal amplitude (ADCs) (/!\\ are those amplitude or charge preamps ???). The timing information provides trajectory determination resulting in momentum per unit charge measurement. Going from a collection of the TDCs to a momentum measurement requires good knowledge of the drift speed and paths followed by the electrons released in the gas. The recorded ADCs give the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, together with the momentum calculated from the trajectory, enables particle identification.

@@

\section{Track Reconstruction}

@@

(TBD)

\begin{thebibliography}{}
\bibitem{CLASref}
B.A. Mecking et al., "The CEBAF large acceptance spectrometer", Nucl. Inst. and Meth. A 503, 513 (2003).

>>>>

\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
\usepackage{graphicx}  
\usepackage{dcolumn}   
\usepackage{bm}        
\usepackage{amssymb}

% avoids incorrect hyphenation, added Nov/08 by SSR
\hyphenation{ALPGEN}
\hyphenation{EVTGEN}
\hyphenation{PYTHIA}

@@

% the following line is for submission, including submission to the arXiv!!
%\hspace{5.2in} \mbox{Fermilab-Pub-04/xxx-E}

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time Projection Chamber for CLAS at JLab}}
\input author_list.tex

\date{\today}

\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
processes, $^4$He remains intact and recoils as a whole in the final state. The 
CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for similar 
studies on proton targets, however it cannot track recoils with momenta less 
than 250 MeV/c. In 2009, we carried out measurements on $^4$He target using
CLAS spectrometer, which was upgraded with a RTPC. The detector was positioned 
directly around the gaseous target, allowing a detection threshold of $~$125  
MeV/c for $^4$He. This article discuses the design of our RTPC, the methods we 
developed to calibrate it and its performances.
\end{abstract}

@@

This paper is organized in this way: section \ref{sec_design} details the design and the internal structure of the RTPC, while section \ref{sec_readout} points the properties of the readout system. The calibration strategies for such detectors will be discussed in section \ref{sec_calib}. Finally, performances are discussed in section \ref{sec_perf}.

\section{Design} \label{sec_design}

@@

\section{Readout System} \label{sec_readout}
The RTPC electron collecting system has 3200 readout pads. These collection elements are located at the end of the amplification region, 69 mm from the central axis.
\begin{figure}[tb]
\centering
%\hspace{-1 cm}
\includegraphics[scale=0.55]{fig/PADs.png}
\caption[]{\small\sf A schematic representation of a part of the readout system. The shaded sixteen pads are a group of pads that are connected to the same pre-amplifier.} 
\label{fig:PADs}
\end{figure}
Figure \ref{fig:PADs} shows a schematic drawing of the size and the alignment configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in width the shift between the rows allows to reduce aliasing. Each half of the RTPC has 40 rows and 40 columns of pads. The shaded region in the figure~\ref{fig:PADs} shows how pads are grouped to the 16 channels pre-amplifiers. The Time to Digital Converter (TDC) units are 114~ns and indicates the time taken by the electron to drift from the ionization point to the readout board. On the the other side, the charge information is measured in Analog-to-Digital-Converter (ADC) units without specific normalization.

@@

\section{Calibration} \label{sec_calib}
Two quantities are recorded for each detected electron at the readout board, time (TDCs) and signal amplitude (ADCs) (/!\\ are those amplitude or charge preamps ???). The timing information provides trajectory determination resulting in momentum per unit charge measurement. Going from a collection of the TDCs to a momentum measurement requires good knowledge of the drift speed and paths followed by the electrons released in the gas. The recorded ADCs give the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, together with the momentum calculated from the trajectory, enables particle identification.

@@

\section{Track Reconstruction}\label{sec_perf}

@@

\input acknowledgement.tex

\begin{thebibliography}{99}

\bibitem{CLASref}
B.A. Mecking et al., "The CEBAF large acceptance spectrometer", Nucl. Inst. and Meth. A 503, 513 (2003).
